---
title: "ShareStats Statistics Taxonomy"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
library(flexdashboard)
```

<script src="copyText.js"></script>

## Assigning taxonomy {.tabset}

### Statistics Taxonomy

To add meta tags to your r-exams markdown file add `exsection:` to the `Meta-information` of your markdown file.

You can ad multiple sections by seperating with a comma. You can copy the desired path from the list below. You may add multiple path by seperation with a comma. No new lines allowed though.

```{}
Meta-information
================
exsection: 
```


```{r, echo=FALSE}
htmltools::includeHTML("taxonomy_list.html")
```

### Meta information

To add meta tags to your r-exams markdown file add ```exextra[]:` to the ```Meta-information` of your markdown file.

We have four categories that can be applied.

* Type: Calculation, Case, Conceptual, Creating graphs, Data manipulation, Interpretating graph, Interpretating output, Performing analysis, Test choice
* Program: SPSS, JASP, R, STATA, Excel, Calculator, Jamovi
* Language: English, Dutch
* Level: Statistical Literacy, Statistical Reasoning, Statistical Thinking 

You can use more than one tag per category. 

```{}
Meta-information
================
exextra[Type]: Calculation, Data manipulation
exextra[Program]: SPSS
exextra[Language]: English
exextra[Level]: Statistical Literacy
```


```{r, echo=FALSE}
library(readxl)
library(DT)
type <- read_excel("source/Taxonomie ShareStats versie 17 maart 2021.xlsx", sheet = 2)

datatable(type[1:9,-2])
```


## ShareStats project

More information on the ShareStats project can be found on [our website](www.sharestats.nl).