---
title: "ShareStats Statistics Taxonomy"
output:
  html_document:
    css: list.css
    toc: true
    toc_float: true
    toc_depth: 2
---

<script src="copyText.js"></script>

## Assigning taxonomy {.tabset}

### Statistics Taxonomy

To add meta tags to your r-exams markdown file add `exsection:` to the `Meta-information` of your markdown file.

You can ad multiple sections by seperating with a comma. You can copy the desired path from the list below. You may add multiple path by seperation with a comma. No new lines allowed though.

```{}
Meta-information
================
exsection: Descriptive statistics / Summary Statistics / Measures of Location / Median, Descriptive statistics / Summary Statistics / Measures of Spread / Standard Deviation
```

#### Click to copy

```{r, echo=FALSE}
htmltools::includeHTML("taxonomy_list.html")
```

### Meta information

To add meta tags to your r-exams markdown file add ```exextra[]:` to the ```Meta-information` of your markdown file.

We have four categories that can be applied.

#### Click to copy

<ol class="bullet">
<li><strong>Type:</strong> 
<span id="calc"  class="tag" onclick="copy_data(calc)">Calculation</span>
<span id="cas1"  class="tag" onclick="copy_data(cas1)">Case</span>
<span id="conc"  class="tag" onclick="copy_data(conc)">Conceptual</span>
<span id="crg"   class="tag" onclick="copy_data(crg)">Creating graphs</span>
<span id="dat"   class="tag" onclick="copy_data(dat)">Data manipulation</span>
<span id="intgr" class="tag" onclick="copy_data(intgr)">Interpretating graph</span>
<span id="intou" class="tag" onclick="copy_data(intou)">Interpretating output</span>
<span id="an"    class="tag" onclick="copy_data(an)">Performing analysis</span>
<span id="tch"   class="tag" onclick="copy_data(tch)">Test choice</span>
</li>
<li>Program: SPSS, JASP, R, STATA, Excel, Calculator, Jamovi</li>
<li>Language: English, Dutch</li>
<li>Level: Statistical Literacy, Statistical Reasoning, Statistical Thinking</li>
</ol>

You can use more than one tag per category. 

```{}
Meta-information
================
exextra[Type]: Calculation, Data manipulation
exextra[Program]: SPSS
exextra[Language]: English
exextra[Level]: Statistical Literacy
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(readxl)
library(DT)
type <- read_excel("source/Taxonomie ShareStats versie 17 maart 2021.xlsx", sheet = 2)

datatable(type[1:9,-2])
```


## ShareStats project

More information on the ShareStats project can be found on [our website](www.sharestats.nl).